DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
control system benchmarks. Additionally, the documentation and videos about \tool are available 
at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.

@@

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer function or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

@@

For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
by the \tool is also stable, as shown in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

@@

\tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 
In particular, the \tool represents the first fully automated synthesis
tool that is algorithmically and numerically sound, considering various error
sources in the implementation of the digital control algorithm and in the computational 
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
digital implementation. 
%
As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).

>>>>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. the stability specification by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using $18$ SISO 
control system benchmarks. Additionally, the documentation and videos about \tool are available 
at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.

@@

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer functions or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

@@

For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
by the \tool also leads to a stable system, as shown in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

@@

The \tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 
In particular, the \tool represents the first fully automated synthesis
tool that is algorithmically and numerically sound, considering various error
sources in the implementation of the digital control algorithm and in the computational 
modeling of plant dynamics~\cite{abate2017,abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
digital implementation. 
%
As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).
